### 2019-07-28 Writeup/PERT_Draft_DPM_7_27.tex
Add the FBBT testing functionality

	For each test case, the timing of the disruption is a discrete random variable sampled from a lognormal distribution, which is commonly used to model failure times~\citep[e.g.,][]{crow1987lognormal,mullen1998lognormal}. The magnitude of the disruption for each activity follows an exponential distribution (which we again sample) whose parameter varies among the activities; the exponential distribution is widely used to model activity durations such as service times~\citep[e.g.,][]{ross1996stochastic}.
	%. The exponential distribution can best model the drastic change caused by a disruption.
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	We compare the quality of five solutions, one from solving model~\eqref{prob:extensive} and four from solving simpler alternatives, to investigate the value of modeling both the random timing and random magnitude of a disruption. First, we can obtain a solution by solving a deterministic model~\eqref{prob:static}, assuming no disruption occurs, i.e., $d^\omega=0$ (denoted ``DET"). Three semi-stochastic alternative models can be solved assuming: both the timing and magnitude of the disruption are deterministic at their expected values (denoted ``EXP"); the timing is random but magnitude is fixed at its expected value (denoted ``\(H\)Only"); and, the magnitude is random but timing is fixed at its expected value (denoted ``\(d\)Only"). Finally, we construct the fully stochastic model~\eqref{prob:extensive} in which both the timing and magnitude are random (denoted ``FULL"). We sample \(500\) scenarios to solve \(H\)Only, \(d\)Only, and FULL. Twenty batches of samples of size 5,000 are used to estimate an upper bound for each candidate solution. The upper bound point estimate for those five candidate solutions is shown in Figure~\ref{fig:value}, and the \(95\%\) confidence interval is shown in Table~\ref{table:value}. \tcr{20 batches of size 5000 for the UB. This is the same as simply using a sample size of 100,000. The point estimates are identical. The sample variance is calculated slightly differently, but is the same in expectation. Right?} \tcb{Yes, the point estimates should have an identical mean no matter how large the sample size is. 20 batches are used just to calculate the variance.} \tcr{But, the point is that the sample variance of the 100,000 points ought to be the same as the sample variance of the 20 batches of 5,000: $\mbox{var} \frac{1}{n} \sum_{i=1}^n X_i = \frac{1}{n} \mbox{var} X_1$.  and $\mbox{var} \frac{1}{\ell} \sum_{j=1}^{\ell} \bar{X}^j_m = \frac{1}{\ell} \mbox{var}  \bar{X}_m = \frac{1}{\ell} \frac{1}{m} \mbox{var} X_1$. So, if $n=$100,000 and $\ell=20$ and $m=$5,000 then it should be the same. In other words, you can compute sample variance of 100,000 points or sample variance of 20 sample means, and it's the same. So, why batch at all? (Here, I've put aside the dividing by $n$ versus $n-1$ in the sample variance calculation, which does create small differences.) For the paper, let's just leave it as you have it. You can delete all these comments.}

>>>>

	For each test case, the timing of the disruption is a discrete random variable sampled from a lognormal distribution, which is commonly used to model failure times~\citep[e.g.,][]{crow1987lognormal,mullen1998lognormal}. The magnitude of the disruption for each activity follows an exponential distribution (which we again sample) whose parameter varies among the activities; the exponential distribution is widely used to model activity durations such as service times~\citep[e.g.,][]{ross1996stochastic}.
	%. The exponential distribution can best model the drastic change caused by a disruption.
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	We compare the quality of five solutions, one from solving model~\eqref{prob:extensive} and four from solving simpler alternatives, to investigate the value of modeling both the random timing and random magnitude of a disruption. First, we can obtain a solution by solving a deterministic model~\eqref{prob:static}, assuming no disruption occurs, i.e., $d^\omega=0$ (denoted ``DET"). Three semi-stochastic alternative models can be solved assuming: both the timing and magnitude of the disruption are deterministic at their expected values (denoted ``EXP"); the timing is random but magnitude is fixed at its expected value (denoted ``\(H\)Only"); and, the magnitude is random but timing is fixed at its expected value (denoted ``\(d\)Only"). Finally, we construct the fully stochastic model~\eqref{prob:extensive} in which both the timing and magnitude are random (denoted ``FULL"). We sample \(500\) scenarios to solve \(H\)Only, \(d\)Only, and FULL. Twenty batches of samples of size 5,000 are used to estimate an upper bound for each candidate solution. The upper bound point estimate for those five candidate solutions is shown in Figure~\ref{fig:value}, and the \(95\%\) confidence interval is shown in Table~\ref{table:value}. 
	%\tcr{20 batches of size 5000 for the UB. This is the same as simply using a sample size of 100,000. The point estimates are identical. The sample variance is calculated slightly differently, but is the same in expectation. Right?} \tcb{Yes, the point estimates should have an identical mean no matter how large the sample size is. 20 batches are used just to calculate the variance.} \tcr{But, the point is that the sample variance of the 100,000 points ought to be the same as the sample variance of the 20 batches of 5,000: $\mbox{var} \frac{1}{n} \sum_{i=1}^n X_i = \frac{1}{n} \mbox{var} X_1$.  and $\mbox{var} \frac{1}{\ell} \sum_{j=1}^{\ell} \bar{X}^j_m = \frac{1}{\ell} \mbox{var}  \bar{X}_m = \frac{1}{\ell} \frac{1}{m} \mbox{var} X_1$. So, if $n=$100,000 and $\ell=20$ and $m=$5,000 then it should be the same. In other words, you can compute sample variance of 100,000 points or sample variance of 20 sample means, and it's the same. So, why batch at all? (Here, I've put aside the dividing by $n$ versus $n-1$ in the sample variance calculation, which does create small differences.) For the paper, let's just leave it as you have it. You can delete all these comments.}
